---
title: "Experiment 1 Pilot Data Integrity"
author: "Dave Braun"
date: "July 19, 2019"
output: 
  html_document:
    df_print: paged
    includes:
      after_body: footer.html
---

This document is dedicated to checking the stimulus presentation and data collection in the pilot of Experiment 1. As of (7-19-2019), two people have completed the Experiment 1 pilot. This will generally be broken down by the two phases of the experiment: *Practice Cued Task Switching* and *Demand Selection Task*.

```{r include = FALSE}
library(tidyverse)
library(data.table)
```


# Practice Cued Task Switching

The data can be viewed below:

```{r}
d <- read.csv('../data/pracCued.csv')
d <- d %>% 
  group_by(workerId) %>% 
  summarize(dummy = n()) %>% 
  mutate(subject = 1:2) %>% 
  select(-dummy) %>% 
  inner_join(d) %>% 
  select(-workerId) %>% 
  rename(workerId = subject)
d
```

I did a visual inspection in Excel, and things appear to be coded correctly. But I'll verify that for a few variables here.

### Transition
This should map on directly to `stimColor` in the data.

```{r}
t <- d %>% 
  mutate(transCheck = ifelse(trialCount == 1, 'startBlock', ifelse(stimColor == shift(stimColor), 'repeat', ifelse(stimColor != shift(stimColor), 'switch', '')))) 
  
sum(t$transCheck == t$transition) == nrow(d)
           
```

```{r}
d %>% 
  filter(transition != 'startBlock') %>% 
  group_by(workerId, transition) %>% 
  summarize('Number of Trials' = n())
```
A few more repetitions per switches, but still within the range of what would be expected on a .5 probability.

### Error
```{r}
t <- d %>% 
  mutate(errorCheck = ifelse(taskCode == 'mag' & stimulus < 5 & responseKey == 'k', 1, 
                             ifelse(taskCode == 'mag' & stimulus > 5 & responseKey == 'j', 1, 
                                    ifelse(taskCode == 'par' & stimulus %% 2 == 1 & responseKey == 'k', 1, 
                                    ifelse(taskCode == 'par' & stimulus %% 2 == 0 & responseKey == 'j', 1, 0)))))
sum(t$errorCheck == t$error) == nrow(d)
```

### Timing Check

```{r}
d %>% 
  group_by(workerId) %>% 
  summarize(TimeMins = max(runTimeMins))
```

### RT Check
```{r}
d %>% 
  filter(rt < 10000) %>% 
  ggplot(aes(x = rt)) + geom_histogram() + xlab('Response Time (ms)') + theme_bw()
```

Looks good.


### Switch Cost
Just peek to see whether we have a switch cost for the two subjects that were run:

```{r}
d %>% 
  mutate(errorTrim = ifelse(error | shift(error), 1, 0)) %>% 
  filter(error == 0, errorTrim == 0, rt < 10000, transition != 'startBlock') %>% 
  group_by(workerId, transition) %>% 
  summarize(rtime = mean(rt), se = sd(rt) / sqrt(n())) %>% 
  ggplot(aes(x = transition, y = rtime)) + 
  geom_bar(stat = 'identity') + 
  geom_errorbar(aes(ymin = rtime - se, ymax = rtime + se), width = 0.5) + 
  facet_wrap(~workerId) + 
  xlab('Transition') + ylab('Response Time (ms)') +
  theme_bw()
```

# Demand Selection Task

## Performance Data

```{r}
d <- read.csv('../data/dst.csv')
d <- d %>% 
  group_by(workerId) %>% 
  summarize(dummy = n()) %>% 
  mutate(subject = 1:2) %>% 
  select(-dummy) %>% 
  inner_join(d) %>% 
  select(-workerId) %>% 
  rename(workerId = subject)
d
```


### Transition
This should map on directly to `stimColor` in the data.

```{r}
t <- d %>% 
  mutate(transCheck = ifelse(trial == 1, 'startBlock', ifelse(stimColor == shift(stimColor), 'repeat', ifelse(stimColor != shift(stimColor), 'switch', '')))) 
  
sum(t$transCheck == t$transition) == nrow(d)
           
```


### Error
```{r}
t <- d %>% 
  mutate(errorCheck = ifelse(task == 'mag' & stimulus < 5 & tolower(cuedResponseKey) == 'k', 1, 
                             ifelse(task == 'mag' & stimulus > 5 & tolower(cuedResponseKey) == 'j', 1, 
                                    ifelse(task == 'par' & stimulus %% 2 == 1 & tolower(cuedResponseKey) == 'k', 1, 
                                    ifelse(task == 'par' & stimulus %% 2 == 0 & tolower(cuedResponseKey) == 'j', 1, 0)))))
sum(t$errorCheck == t$error) == nrow(d)
```


### Timing Check

```{r}
d %>% 
  group_by(workerId) %>% 
  summarize(TimeMins = max(experimentRunTimeMins) - min(experimentRunTimeMins))
```

Worker 2 left and came back to the experiment.


### RT Check
```{r}
d %>% 
  filter(cuedRt < 5000, choiceRt < 500) %>% 
  gather(var, rt, cuedRt, choiceRt) %>% 
  mutate(var = factor(var)) %>% 
  mutate(var = recode(var, "choiceRt" = "Choice", "cuedRt" = "Cued")) %>% 
  ggplot(aes(x = rt)) + geom_histogram() + 
  facet_wrap(~var) + 
  xlab('Response Time (ms)') + ylab('') + 
  theme_bw() + 
  theme(strip.background = element_rect(fill = 'white', color = 'black'))
```

Choice RTs are fast.

## Choice

### Check Left / Right Coding

```{r}
t <- d %>% 
  mutate(keyCheck = ifelse(tolower(choiceResponseKey) == 'd', 'left', ifelse(tolower(choiceResponseKey) == 'f', 'right', '')))

sum(t$keyCheck == t$chosenDeckLocation) == nrow(t)
```

### Check Condition Cycling

```{r}
d %>% 
  group_by(workerId, cycle, block) %>% 
  summarize(condition = unique(condition))
```

```{r}
d %>% 
  group_by(workerId, cycle, block) %>% 
  summarize(leftDeckId = unique(leftDeckId), rightDeckId = unique(rightDeckId))
```


I'm struggling to think of which other assumptions of stimulus presentation need to be checked.

### Looking at some Choice Data

```{r}
d <- d %>% 
  mutate(selectedReferenceDeck = ifelse(chosenDeckId == 'reference', 1, 0))

d %>% 
  unite(cycle_block, cycle, block) %>% 
  mutate(workerId = factor(workerId)) %>%  
  #mutate(workerId = recode(workerId, `1` = 'Subject 1', `2` = 'Subject 2')) %>%  # this line won't be reproducible with larger sample
  group_by(workerId, cycle_block) %>% 
  summarize(selRefDeck = mean(selectedReferenceDeck), se = sd(selectedReferenceDeck) / sqrt(n())) %>% 
  ggplot(aes(x = cycle_block, y = selRefDeck)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = selRefDeck - se, ymax = selRefDeck + se), width = 0.5) + 
  coord_flip() + 
  facet_wrap(~workerId) + 
  xlab('Cycles and Blocks of Experiment') + 
  ylab('Proportion Selection of Reference Deck') + 
  theme_bw() +
  theme(strip.background = element_rect(fill = 'white', color = 'black')) + 
  geom_hline(yintercept = 0.5, linetype = 'dashed') + 
  labs(title = 'Selection Bias', subtitle = 'In each block, how balanced were choices between decks?', caption = 'Facets represent different subjects')
```

```{r}
 d %>% 
  mutate(trialBucket = as.numeric(cut(trial, breaks = seq(0, 100, by = 5)))) %>% 
  group_by(workerId, condition, difference, difficulty, trialBucket) %>% 
  summarize(selRefDeck = mean(selectedReferenceDeck)) %>% 
  ggplot(aes(x = trialBucket, y = selRefDeck, group = condition)) + 
  geom_line(aes(color = difficulty, linetype = difference)) + 
  facet_wrap(~workerId) +
  theme_bw()+
  theme(legend.position = 'top',
        strip.background = element_rect(fill = 'white', color = 'black')) + 
  scale_color_manual(name = 'Difficulty', breaks = c('Easier than Reference', 'Harder than reference'), values = c('Blue', 'Red'), labels = c('Easier than Reference', 'Harder than Reference')) +
  scale_linetype_manual(name = 'Difference', labels = c('Extreme', 'Moderate'), values = c('solid', 'dashed')) +
  xlab('Binned Trial') + 
  ylab('Proportion Selection of Reference Deck') + 
  labs(caption = 'Facets represent different subjects')
  
```



I just want to make sure I have what I need to set up the critical 2 X 2... not that I wanna peek at the effects just yet.

```{r}
condTable <- data.frame(condition = c('EE','EM','HE','HM'), difficulty = c(rep('Easier than Reference', 2), rep('Harder than Reference', 2)), difference = rep(c('Extreme', 'Moderate'), 2))
d %>% 
  group_by(workerId, condition) %>% 
  summarize(selRefDeck = mean(selectedReferenceDeck)) %>% 
  spread(condition, selRefDeck) %>% 
  mutate(EEDEV = abs(EE - EM), EMDEV = abs(EM - 0.5), HMDEV = abs(HM - 0.5), HEDEV = abs(HE - HM)) %>% 
  select(-(EE:HM)) %>% 
  gather(condition, selRefDeck, contains('DEV')) %>%  
  mutate(condition = str_replace(condition, 'DEV', '')) %>% 
  inner_join(condTable) %>% 
  select(-condition) %>% 
  mutate(difference = factor(difference, levels = levels(factor(difference))[c(2,1)])) %>% 
  ggplot(aes(x = difficulty, y = selRefDeck, group = difference)) +
  geom_bar(stat = 'identity', aes(fill = difference), position = position_dodge(width = .9), color = 'black') + 
  facet_wrap(~workerId) + 
  theme_bw() + 
  xlab('Difficulty') +
  ylab('Change in Selection of Reference Deck') +
  labs(caption = 'Facets represent different subjects') + 
  scale_fill_manual(name = 'Difference', values = c(Moderate = 'Black', Extreme = 'Light Grey')) + 
  theme(strip.background = element_rect(fill = 'white', color = 'black'),
        legend.position = 'top')
  
```

Subject 1 is really making me look. Subject 2 indicated that he / she didn't understand the instructions relating to choosing between decks. Maybe I'll add an extra note about that between blocks.














