---
title: "Phase 1: Practice Cued Task Switching"
author: "Dave Braun"
date: "April 8, 2019"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---
This document is dedicated to descriptive analysis of the cued task switching phase from Experiment 1.  
These are pilot data from RAs in the lab collected during the week of 4/1/2019.  
The main goal here is really just to make sure variables in the data look like they're being coded correctly.

```{r include=FALSE}
library(tidyverse)
library(DT)
library(data.table)
```

```{r}
d <- read.csv('../../data/pracCued.csv')
datatable(d, filter = 'top', options = list(pageLength = 5, dom = 't', scrollX = TRUE, scrollCollapse = TRUE, autoWidth = TRUE))
```

## Variable Coding
A breakdown of some of the important variables:  
*Right away, I'm noticing `transition` was coded incorrectly.. But it's easy enough to figure out with `taskCode`, and `transition` looks fine in the other two data files.*  

* `rt` Response time (ms) 
* `taskCode` The task that the participant was cued to respond to
* `stimulus` The actual digit stimulus that appeared on the screen
* `error` Was an error committed? {0 = no, 1 = yes}
* `runTimeMins` The beginning of the phase subtracted from the time stamp on each trial (converted to mins)  
    * So this includes time spent watching the instructional video
* `responseKey` The actual key that was pressed


## Error Rate and Response Time Distribution
Let's check the error rate first to make sure things look reasonable.

```{r}
## forgot that i need to code subject id by hand (from workerId)
d <- d %>% 
  group_by(workerId) %>% 
  summarize(n()) %>% 
  mutate(subject = 1:nrow(.)) %>% 
  inner_join(d, by = 'workerId')
```


```{r}
d %>% 
  group_by(subject) %>% 
  summarize(error = mean(error)) %>% 
  ggplot(aes(x = reorder(subject, error) , y = error)) + geom_bar(stat='identity') + coord_flip() + 
  xlab('Subject') + ylab('Mean Error Rate')
```

Error rates are very low overall. 

```{r}
d$subject <- as.factor(d$subject)
d %>% 
  ggplot(aes(x = rt, group = subject)) + geom_density(aes(fill = subject), alpha = .3) + 
  xlab('Response Time (ms)') +
  theme_bw() + 
  labs(caption = 'Colors map on to different subjects') + 
  theme(legend.position = 'none',
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())
```

These distibutions look very acceptable, good job, RAs.



## Switch Cost
The last thing we can really look for in these data is evidence of the switch cost. I'll break it down by subject since there are only five.

```{r}
d %>% 
  ## coding a correct transition variable
  mutate(transition = ifelse(taskCode == shift(taskCode), 'repeat', 'switch')) %>% 
  filter(error == 0, transition != 'startBlock') %>% 
  group_by(subject, transition) %>% 
  summarize(rTime = mean(rt), sd = sd(rt)) %>% 
  ggplot(aes(x = transition, y = rTime)) + 
  geom_bar(stat = 'identity') + 
  geom_errorbar(aes(ymin = rTime - sd, ymax = rTime + sd)) + 
  labs(caption = 'Bars reflect standard deviations') + 
  xlab('Transition') +
  ylab('Response Time (ms)') + 
  theme_bw() + 
  facet_wrap(~subject)

d %>% 
  ## coding a correct transition variable
  mutate(transition = ifelse(taskCode == shift(taskCode), 'repeat', 'switch')) %>% 
  filter(error == 0, transition != 'startBlock') %>% 
  ggplot(aes(x = transition, y = rt)) + 
  geom_boxplot() + 
  xlab('Transition') +
  ylab('Response Time (ms)') + 
  theme_bw() + 
  facet_wrap(~subject)

```

Looks like switch costs are coming through. The box plot reveals that the large standard deviations in the bar graph are likely driven by RT outliers (> 5000) that I'm not trimming.  

## Final Thoughts
I'm happy with these data overall. Although, I'll have to go back and see what happened with the coding of that transition variable.














